\mytitle

### 2020-07-17 paper.tex
Editted Section 1

In recent years, there has been a growing need to efficiently solve WFLO~
\cite{wilson2014continuous},
while maintaining competitive (albeit not always optimal) solutions. 
The focus on quickly solving the problem was mainly motivated by the fact
that modern farms cover large areas and include hundreds, and
sometimes even thousands, of turbines~\cite{wilson2013learning}. The layout design
process is iterative, computationally expensive, and controlled
by various stakeholders. For each iteration, designers must either
alter an incremental layout or propose a new design
which they have generated by incorporating new constraints and parameter values.
Hence,
one wishes
to solve WFLO interactively at design time, while changing 
many of the input parameter values
and performing a sensitivity analysis to test the impact of those changes~\cite{wilson2018evolutionary}.
The efficient approaches proposed in~\cite{wilson2013learning,wilson2014continuous} do not
take into account the physical model of the wind farm, and hence
do not aim at optimizing the actual energy objective.

In this work, we introduce two novel quadratic WFLO models with the goal 
of combining efficiency, physical farm representation, and optimality. The first
model represents WFLO as a quadratic constrained optimization
problem (QCOP).  The QCOP can be solved using state-of-the-art mathematical solvers
that have been recently extended for such problems, e.g., Gurobi~\cite{gurobi}.  Our
second model is a quadratic unconstrained binary optimization
(QUBO) representation of the WFLO problem.  Such a formulation enables the use of
nascent specialized optimization hardware tailored to solve QUBOs: we use Fujitsu's Digital Annealer (DA) \cite{aramon2019physics}. By employing the two types of advances (software and hardware) for solving
quadratic problems, we enjoy the best of both worlds: 
we are able to provide fast and high performing solutions (in terms of the total energy). Moreover, our approach is based
on a physical model of the wind farm, taking into account
exact calculations of the total energy and the wake effects. 
Therefore, our approach achieves the desired balance between efficiency and effectiveness of the resulting design, in a model-based fashion.
%, a hardware-based
%QUBO solver, to demonstrate the strength of our approach.

@@

Our experiments are focused on the performance of the two approaches
compared to 
existing optimization methods. To this end,
we experiment with 12 standard WFLO benchmark problems (c.f.~\cite{turner2014new})
and show that solving quadratic WFLO models
using Gurobi and the DA
achieves state-of-the-art performance.
%, often outperforming existing solutions when provided sufficient run-time.
Furthermore, we observe that the DA often provides solutions of
similar quality to software-based approaches but with two orders of
magnitude shorter run-time.
%The ability to quickly obtain competitive
%solutions on large WFLO instances can be employed to solve multiple
%wind farm design problems.

The remainder of this paper is structured as follows. Section~\ref{sec:related} presents our wind farm model and a literature review of exact and approximate
optimization solutions to the layout problem. The main contribution, namely the two quadratic models, is introduced in Section~\ref{sec:QUBO4WFLO} and Section~\ref{sec:eval} demonstrates the value of our approach via a thorough empirical evaluation.
%of the proposed methods. 
Lastly, Section~\ref{sec:conclusion} provides concluding remarks and directions for future work.

@@

\section{Discussion and Practical Implications}

>>>>

In recent years, there has been a growing need to quickly find high quality (albeit not always optimal) WFLO solutions~\cite{wilson2014continuous}.
The focus on quickly solving the problem was primarily motivated by the fact
that modern farms cover large areas and include hundreds, and
sometimes even thousands, of turbines~\cite{wilson2013learning}. The layout design
process is iterative, computationally expensive, and controlled
by various stakeholders. For each iteration, designers must either
alter an incremental layout or propose a new design
which they have generated by incorporating new constraints and parameter values.
Hence,
one wishes
to solve WFLO interactively at design time, while changing 
many of the input parameter values
and performing a sensitivity analysis to test the impact of those changes~\cite{wilson2018evolutionary}.

%The efficient approaches proposed in~\cite{wilson2013learning,wilson2014continuous} do not
%take into account the physical model of the wind farm, and hence
%do not aim at optimizing the actual energy objective.

In this work, we introduce two novel quadratic WFLO models with the goal 
of combining efficiency, physical farm representation, and optimality. The first
model represents WFLO as a quadratic constrained optimization
problem (QCOP).  The QCOP can be solved using state-of-the-art mathematical software
that has been recently extended for such problems, e.g., Gurobi~\cite{gurobi}.  Our
second model is a quadratic unconstrained binary optimization
(QUBO) representation of the WFLO problem.  Such a formulation enables the use of
nascent specialized optimization hardware tailored to solve QUBOs: we use Fujitsu's Digital Annealer (DA) \cite{aramon2019physics}. By employing the two types of advances (software and hardware) for solving
quadratic problems, 
we are able to provide fast and high performing solutions (in terms of the total energy). Moreover, our approach is based
on a physical model of the wind farm, taking into account
exact calculations of the total energy and the wake effects. 
Therefore, our approach achieves the desired balance between efficiency and effectiveness of the resulting design, in a model-based fashion.
%, a hardware-based
%QUBO solver, to demonstrate the strength of our approach.

@@

Our experiments are focused on the performance of the two approaches
compared to 
existing optimization methods. To this end,
we experiment with 12 standard WFLO benchmark problems (c.f.~\cite{turner2014new})
and show that solving quadratic WFLO models
using Gurobi and the DA
achieves state-of-the-art performance.
%, often outperforming existing solutions when provided sufficient run-time.
Furthermore, we observe that the DA finds solutions of
similar quality to software-based approaches but with two orders of
magnitude shorter run-time.
%The ability to quickly obtain competitive
%solutions on large WFLO instances can be employed to solve multiple
%wind farm design problems.

The remainder of this paper is structured as follows. Section~\ref{sec:related} presents our wind farm model and a literature review of exact and approximate
optimization solutions to the layout problem. The main contribution, namely the two quadratic models, is introduced in Section~\ref{sec:QUBO4WFLO} and Section~\ref{sec:eval} demonstrates the value of our approach via a thorough empirical evaluation.
%of the proposed methods.
In Section~\ref{sec:discussion}, we discuss the results and their practical implications.
Lastly, Section~\ref{sec:conclusion} provides concluding remarks and directions for future work.

@@

\section{Discussion and Practical Implications}
\label{sec:discussion}
